### 2018-08-07 paper/file-transfer-design.tex
Fixes undefined reference
edits throughout

So far, we have treated the case where Alice sends \emph{one} message to Bob in 
\emph{one} round and any one of Bob's devices receives it.
Now we will consider a slightly different scenario, we will show how to build a 
file transferring service on top of \ac{SPORES}.
Consider that the message \(m\) that Alice wants to send to Bob is too large to 
successfully pass every layer of the route.
\Eg each device goes offline and back online every \(t\) seconds, the bandwidth 
is \(w\) bits per second and the message is \(|m|\) bits; if \(|m| > t w\), 
then the message \(m\) can never be delivered as any device will go offline 
before relaying it to the next node.
The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, 
  m_{n-1}\), where \(|m|/n\leq t w\).
The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
different devices.
The parameters \(t\) and \(w\) must be empirically approximated and used as 
global configuration parameters for the system.
We run simulations for various values of \(t\) and \(w\) in 
\cref{PerformanceAnalysis}.
In this section we describe a file-transfer protocol for splitting a large 
message, sending the fragments using \ac{SPOR} and reassemble them --- even if 
the fragments are received by different devices of the squad.

@@

\commentDaniel{I leave the remaining details for someone else to write up.
  What we need is the details of how Bob's devices syncs and reassembles files.
  Maybe this is reduced to Sprinkler or something.}

>>>>

\sonja{to be merged with the previous subsection}
So far, we have treated the case where Alice sends \emph{one} message to Bob in 
\emph{one} round and any one of Bob's devices receives it.
Now we will consider a slightly different scenario, we will show how to build a 
file transferring service on top of \ac{SPORES}.
Consider that the message \(m\) that Alice wants to send to Bob is too large to 
successfully pass every layer of the route.
\Eg each device goes offline and back online every \(t\) seconds, the bandwidth 
is \(w\) bits per second and the message is \(|m|\) bits; if \(|m| > t w\), 
then the message \(m\) can never be delivered as any device will go offline 
before relaying it to the next node.
The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, 
  m_{n-1}\), where \(|m|/n\leq t w\).
The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
different devices.
The parameters \(t\) and \(w\) must be empirically approximated and used as 
global configuration parameters for the system.
We run simulations for various values of \(t\) and \(w\) in \cref{Performance}.
In this section we describe a file-transfer protocol for splitting a large 
message, sending the fragments using \ac{SPOR} and reassemble them --- even if 
the fragments are received by different devices of the squad.

@@

%\commentDaniel{I leave the remaining details for someone else to write up.
 % What we need is the details of how Bob's devices syncs and reassembles files.
 % Maybe this is reduced to Sprinkler or something.}

### 2018-08-07 paper/security-discussion.tex
edits throughout

\commentDaniel{Predecessor attacks: random walk protocols has the problem that 
  the adversary can see the initiator (statistically) more often than the other 
  nodes, and can thus identify the 
  source~\cite{RoutingSurveyAnonymousProtocols}.
  Our protocol is a \enquote{bounded} random walk, \ie within limits.}

@@

\paragraph*{Security of \ac{SPORES}}

\Ac{SPORES} inherits the security properties from Sphinxes and \ac{SPOR}.
However, both Sphinxes and \ac{SPOR} can be used with any mixing strategy, and 
the security they provide is as secure as the mixing strategy (or flushing 
algorithm) allows.
Since \ac{SPORES} is a fully-fledged system, it must make a concrete choice for 
the mixing strategy.
Since \ac{SPORES} aims at low latency, routers do not batch and mix incoming 
messages; it immediately forwards the messages.
This puts \ac{SPORES} in the same position as Tor~\cite{Tor}, \ie more 
vulnerable to traffic analysis than batching 
mix-nets~\cite{RoutingSurveyAnonymousProtocols} \commentDaniel{we should 
  probably look for the original papers} --- this vulnerability is inherited 
from the mixing strategy.

\Ac{SPORES} also inherits a vulnerability from random-walk protocols and the 
fact that a large message is split into chunks.
Since the chunks can take several paths from source to destination, the source 
will send and the destination will receive more traffic than other nodes in the 
network~\cite{RoutingSurveyAnonymousProtocols} \commentDaniel{we should 
  probably look for the original papers}.
However, this is slightly alleviated by the fact that the source and 
destination can be several different devices --- \ie from the \squad{}s.

@@

A global, passive, network-observing adversary can of course do
statistical disclosure attacks to eventually learn who communicates
with whom~\cite{StatisticalDisclosureAttacks}. \sonja{Daniel: the
  reference seems to be missing}  There are also denial
of service attacks that can lead to the adversary learning more from
the system~\cite{DenialOfSecurity}.  As mentioned in
\cref{system-model}, we share the adversary model with Tor and Sphinx
and thus exclude a global passive adversary. Our focus is on
protecting Alice and Bob from each other and from others who also
participate as nodes in the network, not on protecting them from
surveillance. Nevertheless, we offer some reflections on such an
adversary. We hypothesize that our stateless and redundant design
might yield some advantages over traditional onion routing. For
example, no control messages are sent back to the source if the
adversary has introduced an error.  \sonja{``But these advantages will
  only postpone the success of the attack, eventually even our
  protocol must resend.'' why?}  \commentDaniel{We should look into
  this denial of security.} We would also like to point out that
vulnerability to a global passive attacker is not inherent in Sphinx
or Sphinxes, but can be caused by the way they are applied, \ie the
traffic sent. If performance and resource consumption were not an
issue, batched and well-timed message or file transfer by all nodes
would render traffic analysis pointless.

>>>>

@@

@@

A global, passive, network-observing adversary can of course do
statistical disclosure attacks to eventually learn who communicates
with whom~\cite{StatisticalDisclosureAttacks}. \sonja{Daniel: the
  reference seems to be missing}  There are also denial
of service attacks that can lead to the adversary learning more from
the system~\cite{DenialOfSecurity}.  As mentioned in
\cref{system-model}, we share the adversary model with Tor and Sphinx
and thus exclude a global passive adversary. Our focus is on
protecting Alice and Bob from each other and from others who also
participate as nodes in the network, not on protecting them from
surveillance. Nevertheless, we offer some reflections on such an
adversary. We hypothesize that our stateless and redundant design
might yield some advantages over traditional onion routing. For
example, no control messages are sent back to the source if the
adversary has introduced an error.  \sonja{``But these advantages will
  only postpone the success of the attack, eventually even our
  protocol must resend.'' why?}  \commentDaniel{We should look into
  this denial of security.} Another example is that the source-bounded
random walk and different routes for file chunks make tracking more
difficult than with onion routing circuits. A drawback, however, is
that since the chunks can take several paths from source to destination, the source 
will send and the destination will receive more traffic than other nodes in the 
network~\cite{RoutingSurveyAnonymousProtocols}. However, this is mitigated by the fact that the source and 
destination can be several different devices --- \ie from the \squads.

We would also like to point out that
vulnerability to a global passive attacker is not inherent in Sphinx
or Sphinxes, but can be caused by the way they are applied, \ie the
traffic sent. If performance and resource consumption were not an
issue, batched and well-timed message or file transfer by all nodes
would render traffic analysis pointless. \Ac{SPORES} inherits the security properties from Sphinxes and \ac{SPOR}.
However, both Sphinxes and \ac{SPOR} can be used with any mixing strategy, and 
the security they provide is as secure as the mixing strategy (or flushing 
algorithm) allows.
Since \ac{SPORES} is a fully-fledged system, it must make a concrete choice for 
the mixing strategy.
Since \ac{SPORES} aims at low latency, routers do not batch and mix incoming 
messages; it immediately forwards the messages.
This puts \ac{SPORES} in the same position as Tor~\cite{Tor}, \ie more 
vulnerable to traffic analysis than batching 
mix-nets~\cite{RoutingSurveyAnonymousProtocols} \commentDaniel{we should 
  probably look for the original papers} --- this vulnerability is inherited 
from the mixing strategy.

% \commentDaniel{Predecessor attacks: random walk protocols has the problem that 
%   the adversary can see the initiator (statistically) more often than the other 
%   nodes, and can thus identify the 
%   source~\cite{RoutingSurveyAnonymousProtocols}.
%   Our protocol is a \enquote{bounded} random walk, \ie within limits.}

### 2018-08-07 paper/spor.tex
(Re-)Adds comments to figures in need on updating
edits throughout

Say that Alice wants to send a message \(m\) to Bob.
Bob creates a reply header using \(\CreateReply\) and gives the output to Alice 
over an out-of-band channel.
%We assume that \(m\) is either unavailable when the channel is used or too large to be successfully sent over the channel directly.
At a later point, Alice attaches a message \(m\) to the reply header using 
\(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
reply header as parameter.
\commentAL{Unclear: she sends? Then it reaches Alice?} Then she sends this packet to the first node, which processes it using 
\(\ProcessHeader\).
The node will then process the header and in turn forward the packet to the 
next node.
At some point the message will reach Alice who identifies the message as the 
one expected to come from Bob.
(This process is illustrated in \cref{fig:file-transfer}.)
Now we will focus on how Alice and Bob choose the nodes that they provide to 
\(\CreateReply\) and \(\CreateFwd\).

@@

@@

\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
one uniformly randomly selected node, where.
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(\avail_d(t)\) is the node's probability of being online as a function 
    of time.
\end{itemize}
The \(\GetRandomNode\) algorithm can be instantiated using \eg
Octopus~\cite{Octopus}.
But even a solution like Tor's authoritative directory servers would work,
We will treat \(\avail_d\) in \cref{sec:squad_overlay}.

>>>>

Say that Alice wants to send a message \(m\) to Bob.
Bob creates a reply header using \(\CreateReply\) and gives the output to Alice 
over an out-of-band channel.
%We assume that \(m\) is either unavailable when the channel is used or too large to be successfully sent over the channel directly.
At a later point, Alice attaches a message \(m\) to the reply header using 
\(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
reply header as parameter. \sonja{what about the crossover node and
  Alice's leg of the route?} 
Then she sends this packet to the first node, which processes it using 
\(\ProcessHeader\).
The node will then process the header and in turn forward the packet to the 
next node.
At some point the message will reach Bob who identifies the message as the 
one expected to come from Alice.
(This process is illustrated in \cref{fig:file-transfer}.)
Now we will focus on how Alice and Bob choose the nodes that they provide to 
\(\CreateReply\) and \(\CreateFwd\).

@@

\commentAL{When is CreateHeader used?}

@@

\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
one uniformly randomly selected node, where.
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(\avail_d(t)\) is the node's probability of being online as a function 
    of time.
\end{itemize}
The \(\GetRandomNode\) algorithm can be instantiated using \eg
Octopus~\cite{Octopus}. Its function is analogous to 
Tor's authoritative directory servers, but we need a decentralized system. 
We will treat \(\avail_d\) in \cref{sec:squad_overlay}.

### 2018-08-07 paper/squad-overlay-design.tex
figures!
edits throughout

\newcommand\fileid{\ensuremath{ID_{\text{f}}}\xspace}
\newcommand\sendingdevice{\ensuremath{d^{(s)}_f}\xspace}
\newcommand\recdevice{\ensuremath{d^{(r)}_f}\xspace}

@@

The exchanged data forms a sequence, ordered by timestamp, populated by three types of information:
\begin{itemize}
	\item \texttt{CONNECTED<$d, t_{step}$>}: Sent by device $d$ when it is used by its user at time step\footnote{As far as devices connections are concerned, time is discretized: we consider that each interaction lasts the same time.} $t_{step}$. $d$ is otherwise considered offline at this time. Devices use this information to predict their probability of remaining online, as presented in section~\ref{ssec:device_availability};
	\item \texttt{SENDING<\sendingdevice, \fileid>}: When the user decides to send a file $f$ located on a device \sendingdevice, \sendingdevice informs its peers of this fact, and joins the file ID \fileid. Squad members will use this information to forward acknowledgments from the remote to \sendingdevice;
	\item \texttt{RECEIVING<\recdevice, \fileid>}: Reciprocally, when the user starts receiving a file $f$ onto a device \recdevice, \recdevice informs its peers of this fact, and joins the file ID \fileid. Squad members will use this information to forward the file's content from the remote to \recdevice.
\end{itemize}

Given this information dissemination and history reconciliation mechanism, each \squad member knows the full sequence $S$ at all time with an overwhelming probability, even in the face of churn~\cite{luxey:cascade}.

@@

The predictive nature of \name lies in the fact that each participating device publicly advertises its probability of being connected in the near future. 
This information is used when any node needs to create a Probabilistic Onion Route (POR), as will be shown in the next subsection~\ref{ssec:por}.

@@

$P'd$ will be advertised in spite of $P_d$. It will also be used as a baseline in the evaluation.

\subsection{Probabilistic Onion Routes}
\label{ssec:por}

@@

\newcommand\rpsview{\ensuremath{\mathcal{V}}\xspace}
\newcommand\desc{\ensuremath{{\mathtt{desc}}}\xspace}

@@

%\newcommand\layer{\ensuremath{{\mathcal{L}}}\xspace}
\newcommand\layer{L\xspace}
\newcommand\Poff{\ensuremath{P_{\text{off}}}\xspace}

@@

\newcommand\finfo{\ensuremath{\mathcal{I}_f}}
\newcommand\filesize{\ensuremath{s_f}\xspace}
\newcommand\chunksize{\ensuremath{s_{\text{chunk}}}\xspace}
\newcommand\nchunks{\ensuremath{n_{\text{chunks}}}\xspace}
\newcommand\hashchunk{\ensuremath{h_{\text{chunk}}}\xspace}
\newcommand\hashfile{h\xspace}

@@

Our file transfer protocol is loosely based on BitTorrent \cite{bt_bep3}: 
at initialization, a file $f$ of size \filesize is first cut into chunks of constant size \chunksize by its uploader,
resulting in $\nchunks = \lceil \filesize / \chunksize \rceil$ chunks.
A SHA1 hash \hashchunk is computed for each chunk, plus another SHA1 hash \hashfile of the chunks hashes ; that will serve error detection.

@@

\newcommand\bitfield{\ensuremath{bf_f}\xspace}
\newcommand\tupload{\ensuremath{t_{\text{upload}}}\xspace}

@@

Bob receives $f$ on a device \recdevice, but a chunk $c_i$ for $f$ might arrive on any of his devices. 
This device then fetches the address of the proper recipient \recdevice by looking for the line \texttt{RECEIVING<\recdevice, \fileid>} in its squad sequence, 
and forwards the file chunk to \recdevice.
Upon reception of the chunk, \recdevice verifies its integrity by computing its SHA1 hash $h_{c_i}$ and comparing it to $\finfo.h_{c_i}$.
If the chunk is valid, \recdevice updates its \emph{bitfield} \bitfield: this bit-array of size \nchunks is initialized with 0;
every time Bob successfully receives a chunk $c_i$, \recdevice sets the bit $\bitfield[i]$.
To acknowledge the chunk's reception, \recdevice sends \bitfield back to Alice, through a unique route $\mathcal{H}'_{c_i}$.

>>>>

@@

The exchanged data forms a sequence, ordered by timestamp, populated by three types of information:
\begin{itemize}
	\item \texttt{CONNECTED<$d, t_{step}$>}: Sent by device $d$ when it is used by its user at time step\footnote{As far as devices connections are concerned, time is discretized: we consider that each interaction lasts the same time.} $t_{step}$. $d$ is otherwise considered offline at this time. Devices use this information to predict their probability of remaining online, as presented in section~\ref{ssec:device_availability};
	\item \texttt{SENDING<\sendingdevice, \fileid>}: When the user decides to send a file $f$ located on a device \sendingdevice, \sendingdevice informs its peers of this fact, and joins the file ID \fileid. \Squad members will use this information to forward acknowledgments from the recipient to \sendingdevice;
	\item \texttt{RECEIVING<\recdevice, \fileid>}: Reciprocally, when the user starts receiving a file $f$ onto a device \recdevice, \recdevice informs its peers of this fact, and joins the file ID \fileid. \Squad members will use this information to forward the file's content from the sender to \recdevice.
\end{itemize}

Given this information dissemination and history reconciliation mechanism, each \squad member knows the full sequence $S$ at all times with an overwhelming probability, even in the face of churn~\cite{luxey:cascade}.

@@

The predictive nature of \name lies in the fact that each participating device publicly advertises its probability of being connected in the near future. 
This information is used when any node needs to create a Stateless Predictive Probabilistic Onion Route (\SPOR), as will be shown in the next subsection~\ref{ssec:por}.

@@

$P'd$ will be advertised in spite of $P_d$. It will also be used as a baseline in the evaluation.
\sonja{this and the next subsection seem redundant and need to be merged}
\subsection{Stateless Predictive Probabilistic Onion Routes}
\label{ssec:por}

@@

@@

@@

@@

Our file transfer protocol is loosely based on BitTorrent \cite{bt_bep3}: 
at initialization, a file $f$ of size \filesize is first cut into chunks of constant size \chunksize by its uploader,
resulting in $\nchunks = \lceil \filesize / \chunksize \rceil$ chunks.
A SHA1 hash \hashchunk is computed for each chunk, plus another SHA1 hash \hashfile of the chunks hashes; that will serve error detection.

@@

@@

Bob receives $f$ on a device \recdevice, but a chunk $c_i$ for $f$ might arrive on any of his devices. 
This device then fetches the address of the proper recipient \recdevice by looking for the line \texttt{RECEIVING<\recdevice, \fileid>} in its \squad sequence, 
and forwards the file chunk to \recdevice.
Upon reception of the chunk, \recdevice verifies its integrity by computing its SHA1 hash $h_{c_i}$ and comparing it to $\finfo.h_{c_i}$.
If the chunk is valid, \recdevice updates its \emph{bitfield} \bitfield: this bit-array of size \nchunks is initialized with 0;
every time Bob successfully receives a chunk $c_i$, \recdevice sets the bit $\bitfield[i]$.
To acknowledge the chunk's reception, \recdevice sends \bitfield back to Alice, through a unique route $\mathcal{H}'_{c_i}$.
